### 2016-08-17 transformation.tex
remove by Chen

Even for the restrictive case above, the mixed-integer linear programming (MILP) approach by Nelissen et al. \cite{ecrts15nelissen} does not provide the exact worst-case response time. 
However, if we apply the characteristics of the worst-case release pattern provided in Lemma 2 by Nelissen et al. \cite{ecrts15nelissen},  the exact worst-case response time can be calculated by exploring all  release patterns that satisfy these conditions. Detailed discussions can be found in a recent report by Chen \cite{Chen2016b}. In fact, it has recently been shown that verifying the schedulability of such a task set is coNP-hard in the strong sense even in the considered simplified case~\cite{RTSS2016-suspension}. Therefore, analyzing the exact worst-case response time of task $\tau_k$ is NP-hard in the strong sense by following the same proof by Chen \cite{RTSS2016-suspension}.

>>>>

Even for the restrictive case above, the mixed-integer linear programming (MILP) approach by Nelissen et al. \cite{ecrts15nelissen} does not provide the exact worst-case response time. 
However, if we apply the characteristics of the worst-case release pattern provided in Lemma 2 by Nelissen et al. \cite{ecrts15nelissen},  the exact worst-case response time can be calculated by exploring all  release patterns that satisfy these conditions. Detailed discussions can be found in a recent report by Chen \cite{Chen2016b}. In fact, it has recently been shown that verifying the schedulability of such a task set is coNP-hard in the strong sense even in the considered simplified case~\cite{RTSS2016-suspension}. Therefore, analyzing the exact worst-case response time of task $\tau_k$ is NP-hard in the strong sense by following the same proof \cite{RTSS2016-suspension}.
